Data Pre-Processing

### 2021-04-21 AST-Framing-Ontario/Data Pre-Processesing.rmd
April 21 Updates

Instructions are provided below for processing a single folder of PDF documents, as a walkthough of the processing techniques used. Another set of instructions is provided at the end of this notebook that allows for the processing multiple folders simultaneously. (*Jason, you can add the content from 'Multiple PDF Files to Corpus.Rmd' to the sections below*)

@@

```{r}
pdfLocation <- "E:/Github/AST-Framing-Analysis-Ontario/Consortium"

@@

NAwords <- c("school", "transportation", "can", "use", "active", "et al", "travel", "j", "behav" , "nutr", "phys", "int", "n", "elsevier", "na", "sciencedirect", "journal", "transport", "mode", "modes", "children", "s")
corpus <- tm_map(corpus, removeWords, NAwords)
corpus <- tm_map(corpus, removeNumbers)

@@

## NLP Analysis

Latent Dirichlet Allocation (LDA) (*Jason: can you explain what this means*?)
This algorithm 
```{r}
# k represents the number of topics to be generated by the algorithm 
k <- 4
lda <- LDA(DTM, k, control = list(seed = 1234))

@@

top_terms %>% 
  mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot(aes(beta, term, fill = factor(topic))) + 
  geom_col(show.legend = FALSE) + 
  facet_wrap(~topic, scales = "free") + 
  scale_y_reordered() +
  scale_x_continuous(limits = c(0,0.06))

LDA using multiple seeds

@@

@@

@@

This code is a is a version of the code in the 'AST-Framing-Ontario.Rmd'. It is compressed into a single block to allow the iterative conversion each subfolder. Corpus' will be cleaned for white spaces, punctuations, English stopwords, and converted to lowercases. Any additional stopwords will need to be removed manually as the user sees fit. 
```{r}
# Iterating through each subfolders 
m <- 1
for (subFolder in subFolders){

@@

Creating Term-Document Matrix and Document-Term Matrix with the fully cleaned  corpuses 
```{r}
# n - number of corpuses
n <- 3
for (i in seq(1, n, 1))
{
tempCorpus <-  eval(parse(text = paste("corpus", toString(i), sep = "")))
TDM <- TermDocumentMatrix(tempCorpus)
DTM <- DocumentTermMatrix(tempCorpus)
matrix1 <- as.matrix(TDM)
matrix2 <- as.matrix(DTM)

>>>>

Instructions are provided below for processing a single folder of PDF documents, as a walkthough of the processing techniques used. Another set of instructions is provided at the end of this notebook that allows for the processing multiple folders simultaneously.

@@

```{r}
pdfLocation <- "E:/Github/AST-Framing-Analysis-Ontario/Municipalities or Regions"

@@

NAwords <- c("school", "transportation", "can", "use", "active", "et al", "travel", "j", "behav" , "nutr", "phys", "int", "n", "elsevier", "na", "sciencedirect", "journal", "transport", "mode", "modes", "children", "s", "the")
corpus <- tm_map(corpus, removeWords, NAwords)
corpus <- tm_map(corpus, removeNumbers)

@@

## Natural Languange Processing (NLP) Analysis

NLP is a way to correlate words across a collection of texts or corpus.

Topic Modelling with Latent Dirichlet Allocation (LDA)

The goal of topic modelling is to identify the re-occurring themes in our corpus quantitatively with code. The code below utilizes LDA, an algorithm that when provided a number of desrete topics, 'k', will calculate the likelyhood of any given term being generated in a given topic. This algorithm runs under the 'bag of words' assumptions with means grammatic structre (adjective, noun, verb) is not considered. Words are rather considered 
```{r}
# k represents the number of topics to be generated by the algorithm 
k <- 5
lda <- LDA(DTM, k, control = list(seed = 1234))

@@

# Beta represents the probability of 'term' being generated in topic 'n' 
# Topics are generated by the LDA algorithm, its is up to the user to interpret the context of the topics 
terms(lda,15)
top_terms %>% 
  mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot(aes(beta, term, fill = factor(topic))) + 
  geom_col(show.legend = FALSE) + 
  facet_wrap(~topic, scales = "free") + 
  scale_y_reordered() +
  scale_x_continuous(limits = c(0,0.06))

```
LDA using multiple seeds

@@

Here we examine texts based on the structural relationship of a sequence of words. We can tokenize n-grams, where 'n' represents the number of consecutive words, to chart what group of words most frequently occur in our corpus.

@@

Word cloud is a nice visual way to view the most common words in your text document matrix

@@

This code is a is a version of the code in the 'AST-Framing-Ontario.Rmd'. It is condensed into a single block to allow the iterative conversion each subfolder. Corpora will be cleaned for white spaces, punctuations, English stopwords, and converted to lowercases. Any additional stopwords will need to be removed manually as the user sees fit. 
```{r}
# Iterating through each subfolders 
m <- 1
for (subFolder in subFolders){

@@

Creating Term-Document Matrix and Document-Term Matrix with the fully cleaned  corpuses 
```{r}
# n - number of corpora
n <- 3
for (i in seq(1, n, 1))
{
tempCorpus <-  eval(parse(text = paste("corpus", toString(i), sep = "")))
TDM <- TermDocumentMatrix(tempCorpus)
DTM <- DocumentTermMatrix(tempCorpus)
matrix1 <- as.matrix(TDM)
matrix2 <- as.matrix(DTM)
